\documentclass{ximera}
\title{Question and answer types}
\begin{document}

\begin{abstract}
  This section explores the different types of exercises Ximera supports. 
\end{abstract}

\maketitle

Ximera supports many exercise types.


\section{Basic Function Answer Type}

Verbatim environments look worse:

\begin{verbatim}
         $3\times 2 = $ \answer{6}
\end{verbatim}

But this code should produce a question with an answer box:

\begin{question}
  $3\times 2 = $ \answer{6}
\end{question}


In addition to numerical answers, we also support elementary functions:

\begin{verbatim}
    \begin{question}
         $ \frac{\partial}{\partial x} x^2\sin(y) = $ \answer{2xsin(y)}
    \end{question}
\end{verbatim}

Produces:

\begin{question}
  $ \frac{\partial}{\partial x} x^2\sin(y) = $ \answer{2xsin(y)}
\end{question}

Remarks are working well (one of many theorem types):

\begin{remark}
Under the hood, Ximera is parsing the user input, producing a
function, and checking the user input function against ``answer'' at
$100$ different complex numbers, and seeing if the results are
``reasonably'' close to each other.  We compare the complex extensions
of these functions to circumvent domain issues.
\end{remark}

We also support matrices of expressions in answers.

\begin{verbatim}
\begin{question}
Enter the matrix  \(\begin{bmatrix} x & y \\ xy & z+1 \end{bmatrix}\)
    \begin{matrixAnswer}
	    correctMatrix = [['x','y'],['xy','z+1']]
    \end{matrixAnswer}
\end{question}
\end{verbatim}

This should eventually convert to a +/- matrix answer widget.

\begin{question}
  Enter the matrix  \(\begin{bmatrix} x & y \\ xy & z+1 \end{bmatrix}\)
\begin{matrixAnswer}
    correctMatrix = [['x','y'],['xy','z+1']]
\end{matrixAnswer}
   % This doesn't seem to compile?
\end{question}

\begin{remark}
  The plus and minus buttons add and subtract columns or rows.  
\end{remark}



\section{Multiple Choice Answer Type}

\begin{verbatim}
\begin{question}
Which of the following functions has a graph which is a parabola?
  \begin{multipleChoice}
    \choice[correct]{$y=x^2+3x-3$}
    \choice{$y = \frac{1}{x+2}$}
    \choice{$y=3x+1$}
  \end{multipleChoice}
\end{question}
\end{verbatim}

Multiple choice questions seem to be working:

\begin{question}
  Which of the following functions has a graph which is a parabola?
  \begin{multipleChoice}
    \choice[correct]{$y=x^2+3x-3$}
    \choice{$y = \frac{1}{x+2}$}
    \choice{$y=3x+1$}
  \end{multipleChoice}
\end{question}

\begin{remark}
  Multiple choice questions are automatically shuffled.
\end{remark}



\section{Free-response}

The free response environment gives students access to a \LaTeX\ editor. 

Free response does not work as intended:

\begin{freeResponse}
  This is the model solution.
\end{freeResponse}

\begin{remark}
Clicking on \verb!View model solution! shows the user
whatever you typed in the  \verb!freeResponse! environment.
\end{remark}

\section{Example}

\begin{example}
This is an example.
\end{example}
\begin{explanation}
This is an explanation.
\end{explanation}

\section{Prompt}

\begin{prompt}
This is a prompt.
\end{prompt}

\section{Code}

\begin{code}
This is in code environment.
This is on the second line.
This is on the third line.
\end{code}

\begin{python}
This is in a python environment.
This is on the second line.
This is on the third line.
\end{python}

\section{Parts}

The parts environment should be removed.

\begin{parts} %this will be deprecated
\item Part 1
\item Part 2
\end{parts}

\section{Shuffle}

We need to figure out what the shuffle environment does.

\begin{shuffle}
This is a shuffle environment. What goes here?
\end{shuffle}



\section{Solution}

The solution environment should be removed.

\begin{solution} %this will be deprecated
What is this?
\end{solution}

\section{Interactive}

We need to figure out what the interactive environment does.

\begin{interactive}
What is this?
\end{interactive}



\section{Feedback}

We need to figure out what the feedback environment does.

\begin{feedback}
What is this?
\end{feedback}



\section{Dialogue}

Dialogue is working as intended:

\begin{dialogue}
\item[Nathan] What is this?
\item[Hans] This is for showing a conversation.
\end{dialogue}



\section{Theorems}

\begin{theorem}
What is this? (there are other theorems)
\end{theorem}

Maybe we want to list the other theorems?



\section{Word Choice}

We need to figure out how word choice works.

\wordChoice[wrong1, wrong2]{right}


\section{Linking}

video, youtube don't work in html
link{with a link here} works
link{} links back to same page online, how does this work?

\video{https://www.youtube.com/watch?v=dQw4w9WgXcQ} %doesn't work in html
\youtube{https://www.youtube.com/watch?v=dQw4w9WgXcQ} %doesn't work in html
\link{https://www.youtube.com/watch?v=dQw4w9WgXcQ} %works
\link{} %links to same page online, does nothing in pdf



\section{Metadata}

There is some metadata here. (prerequisites, outcomes to be figured out later)

\prerequisites{This is a prerequisite} %metadata

\outcome{This is an outcome.} %metadata



\section{Problem Types}

\begin{xarmaBoost}
A problem worth Xarma.
\end{xarmaBoost}

\begin{question}
This is a question?
\end{question}

\begin{problem}
This is a problem.
\end{problem}

\begin{exercise}
This is an exercise.
\end{exercise}

\begin{exploration}
This is an exploration.
\end{exploration}

\end{document}
